---
title: "tut04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question 1

##1. Assign each of the 25359 restaurants to have S3 class restaurant in R. You should now have a list of restaurant objects of length 25359.
```{r}
library(jsonlite)
fname <- "../data/restaurants_dataset.json"
rest_lines <- readLines(fname)
rest_json <- lapply(rest_lines, fromJSON)
class_func<-function(x){
  class(x)<-"restaurant"
  return (x)
}
rest_class_list<-lapply(rest_json,class_func)
```

## creating summary function

#cat is used instead of print(character vector is returned)
```{r}
summary.restaurant<-function(x){
  str<-paste(x$name,"was graded",length(x$grades$grade), "times")
  cat(str)
}
```
##Create a simple feature object rest_sf that contains a row for each restaurant
```{r}
names<-sapply(rest_json,function(x) x$name)
cuisine<-sapply(rest_json,function(x)x$cuisine)
boroughs<-sapply(rest_json,function(x)x$borough)
coordinates<-sapply(rest_json,function(x)x$address$coord)
filter_out <- function(x) {
  if ((class(x) == "numeric")) {
    return(x)
  } else {
    return(NA)
  }
}
library(sf)
coordinates <- sapply(coordinates, function(x) filter_out(x))
lat <- sapply(coordinates, function(x) x[1])
long <- sapply(coordinates, function(x) x[2])
combine <- data.frame(cbind(names,boroughs,cuisine,lat,long))
rest_sf <- st_as_sf(combine, coords = c("lat","long"), crs = 4326, na.fail = FALSE)
plot(st_geometry(rest_sf),axes=TRUE)
```
##Problems with data

Coordinates are  missing for some of the observations
The cuisines are sometimes listed as "Not Listed/Not Applicable"
There are 51 boroughs which are stated as "Missing" in our data
#all_bor<-sapply(rest_class_list,function(x)x$borough)
#borough_missing <- str_detect(all_bor, "Missing")
#length(which(borough_missing))

From our plot above there seems to be a few distinct outliers which possibly implies that the coordinates indicated are not in New York City. In this case, the coordinates may be wrongly indicated in the dataset.

##MAS API
```{r}
library(jsonlite)
url<-"https://eservices.mas.gov.sg/api/action/datastore/search.json?resource_id=7f1363cc-3875-4e03-a389-fc47342bb840&limit=342"
mas_list<-fromJSON(url)
mas_data<-mas_list$result$records
start<-as.Date("1992-02-01")
mas_data$end_of_month<-seq.Date(start,length=342,by="1 month")-1
plot(mas_data$end_of_month,as.numeric(mas_data$cards_main)/1e6,main="Number of cards",type="l",xlab="Month",ylab="No.of cards(millions)",col="purple",las=2,xaxt='n')
lines(mas_data$end_of_month,as.numeric(mas_data$cards_supp)/1e6,type="l",col="red")
legend("topleft",legend=c("Main","Supp"),lty=1,col=c("purple","red"))
x_seq<-seq(1,342,by=12)
x_intervals<-mas_data$end_of_month[x_seq]
axis(side=1,at=x_intervals,labels=strftime(x_intervals,format="%b-%y"))





#Convert to dataframe
as.data.frame()

















```